Relaxed Weak Accelerated Proximal Gradient Method: a Unified Framework for Nesterov's Accelerations

### 2025-09-12 Notebook LaTEX/R-WAPG/2025-06-10-00-paper.tex
>w<, changes

    It is called \emph{Free R-WAPG} because it doesn't require any knowledge of $\mu, L$ in prior for the smooth part $f$, making it parameter-free.

>>>>

    \textcolor{purple}{
        We can do this because all convex function is $\mu = 0$ strongly convex. 
        With $\mu = 0$, it has from Definition \ref{def:rwapg-seq} that for all $k \ge 0$: 
        \begin{enumerate}[nosep]
            \item It allows $\alpha_k \in (0, 1)$. The sequence $(\alpha_k)_{k \ge 1}$ is as loose as possible. 
            \item It has $\rho_{k - 1} = \alpha_k/((1 - \alpha_k)\alpha_{k - 1}^2)$, hence $(1 - \alpha_k)\rho_{k - 1} = \alpha_k^2/\alpha_{k - 1}^2$. 
        Hence, the big product in Proposition \ref{prop:wapg-convergence} simplifies into
            \prod_{i = 0}^{k - 1}
            \max(1, \rho_i)(1 - \alpha_{i + 1})
            \prod_{i = 0}^{k - 1}
            \max(1 - \alpha_{i + 1}, \rho_i(1 - \alpha_{i + 1}))
            \prod_{i = 0}^{k - 1}
                1 - \alpha_{i + 1}, \frac{\alpha_{i + 1}^2}{\alpha_i^2}\right). 
        Finally, since $\mu = 0$, Propisition \ref{prop:r-wapg-momentum-repr} applies with the momentum term simplifies into $\alpha_{k + 1}(\alpha_k^{-1} - 1)$. 
    Below, we define \emph{Free R-WAPG}. 

### 2025-09-12 Notebook LaTEX/R-WAPG/presentation.tex
>w<, changes

                    & \alpha_k \in (\mu, 1] \quad (\forall k \ge 1). 

@@

@@

@@

            The parameters in this specific trial are are $\mu = 7.432363627613958\times 10^{-18}$ and $L = 2321.737206983643$. 

@@

>>>>

                    & \alpha_k \in (\mu/L, 1] \quad (\forall k \ge 1). 

@@

        \begin{frame}{Introducing numerical experiments}
            All convex functions are strongly convex with strong convexity constant $\mu = 0$. 
            With $\mu = 0$, it has from Definition \ref{def:rwapg-seq} that for all $k \ge 0$: 
                \item It allows $\alpha_k \in (0, 1)$. The sequence $(\alpha_k)_{k \ge 1}$ is as loose as possible. 
                \item It has $\rho_{k - 1} = \alpha_k/((1 - \alpha_k)\alpha_{k - 1}^2)$, hence $(1 - \alpha_k)\rho_{k - 1} = \alpha_k^2/\alpha_{k - 1}^2$. 
            This simplifies our convergence claim into: 
                \prod_{i = 0}^{k - 1}
                \max(1, \rho_i)(1 - \alpha_{i + 1})
                &= 
                \prod_{i = 0}^{k - 1}
                \max(1 - \alpha_{i + 1}, \rho_i(1 - \alpha_{i + 1}))
                &= 
                \prod_{i = 0}^{k - 1}
                \max\left(
                1 - \alpha_{i + 1}, \frac{\alpha_{i + 1}^2}{\alpha_i^2}\right). 
            This insipired our numerical experiments. 

@@

        \begin{frame}{Real time R-WAPG upper bound}
            By collecting $(\alpha_k)_{k \ge 0}$ while the algorithm is running we made the following plot for the simple quadratic experiment. 
                \begin{subfigure}[b]{0.75\textwidth}
                    \includegraphics[width=\textwidth]{
                        assets/simple_regression_rwapg_upperbnd_1024.png
                    $N = 1024$, the upper bound estimates in real time from the collected $(\alpha_k)_{k \ge 0}$ sequence. 
                \label{fig:simple-quadratic-r-wapg-rwapg-upperbnd}

@@

            The parameters in this specific trial are $\mu = 7.432363627613958\times 10^{-18}$ and $L = 2321.737206983643$. 

@@

        \begin{frame}{Real time R-WAPG upper bound}
            Below is the plot of the real time estimates of R-WAPG convergence bound using for the LASSO experiment. 
                \begin{subfigure}[b]{0.75\textwidth}
                    \includegraphics[width=\textwidth]{
                        assets/lasso_rwapg_upperbnd_256.png
                    $N = 1024$, the upper bound estimates in real time from the collected $(\alpha_k)_{k \ge 0}$ sequence. 
                \label{fig:single-lass-r-wapg-rwapg-upperbnd}
